---
title: "wrapup1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(MASS)
library(lubridate)
library(plotly)
source('./R/its_outputs.R')
source('./R/control_outputs.R')

source('./R/scale.fun.R')
source('./R/run_its.R')
source('./R/run_control.R')

```

```{r}
a1 <- 
  read.csv('./Data/monthly_mortality_10_countries.csv')

a2 <- a1 %>% 
  rename(J12_J18= J12_J18_prim,
         acm_noresp_nodiar =acm_noj_nodiarr_prim,
         date=monthdate) %>%
  dplyr::select(date,age_group, J12_J18, acm_noresp_nodiar, E40_E46_prim,E70_E90_prim,A30_49_prim, C00_D48_prim, K00_K99_prim, V01_X59_prim) %>% 
  filter( grepl('2-59m A', age_group))

```

Vaccine introduction:
Peru: PCV7 Aug 2009, PCV10 Dec 2011
Ecuador: PCV7 Aug 2010, PCV10 (2+1) Feb 2011, PCV10(3+0 Feb 2014) 
Colombia PCV10 (2+1)" Nov 2011
Mexico PCV7 (2+1 Feb 2008); PCV13 (2+1) Feb 2011


Set parameters here for the model
```{r}
vax.intro.date= as.Date('2008-02-01')

months_until_second_knot = 12 #how many months between vaccine intro and start of eval period

months_until_third_knot = 36  #if there is a 2nd change in slope, how many months after vaccine intro does it occur? if no 2nd change, set as 999

ds= 'mx' #mx=Mexico, pr=Peru, ec=Ecuador, co=Colombia
```


```{r}

#form_its1 <- as.formula ("J12_J18 ~ month+ index + spl1 + spl2 + spl3 + acm_noresp_nodiar")

form_its1 <- as.formula ("J12_J18 ~ month+ index + spl1 + spl2  +spl3 + offset(acm_noresp_nodiar)")


mod1 <- run_its(set.vax.intro.date= vax.intro.date, set.form_its1=form_its1, months_until_third_knot=months_until_third_knot, months_until_second_knot=months_until_second_knot )

summary(mod1$mod1)

mod1$mod1$aic #AIC score

```

Run this function to generate uncertainty intervals and summary stats for the ITS model

```{r}
mod1.outputs <- its_outputs(mod1)

```

Ratio for entire evaluation period

```{r}
mod1.outputs$rr.q.post
```

Rate ratio over time from ITS
```{r}
mod1.outputs$p.rr.trend +ggtitle('Rate Ratio over time following vaccine introduction')
```

Observed vs expected by month. Observed=red; black=fitted; gray shaded area=counterfactual
```{r}
mod1.outputs$p.preds
```

Observed vs expected by year Observed=red; black=fitted; gray shaded area=counterfactual
```{r}
mod1.outputs$p.preds.agg
```

Cumulative cases prevented
```{r}
ggplotly(mod1.outputs$p.cum_prevented)
```


## Model 2: ITS models with controls
```{r}

#form_its1 <- as.formula ("J12_J18 ~ month+ index + spl1 + spl2 + spl3 + acm_noresp_nodiar")

form_its1 <- as.formula ("J12_J18 ~ month+ index + spl1 + spl2  +E70_E90_prim + E40_E46_prim+ A30_49_prim + C00_D48_prim + K00_K99_prim + V01_X59_prim + offset(acm_noresp_nodiar)")

mod2 <- run_its(set.vax.intro.date= vax.intro.date, set.form_its1=form_its1, months_until_third_knot=months_until_third_knot, months_until_second_knot=months_until_second_knot )

summary(mod2$mod1)

mod2$mod1$aic #AIC score

```


## Model 3: Fit to pre-period, and project forward (similar to synthetic controls)
```{r}

form_control <- as.formula ("J12_J18_pre ~ month+ index   +E70_E90_prim + E40_E46_prim+ A30_49_prim + C00_D48_prim + K00_K99_prim + V01_X59_prim + acm_noresp_nodiar")

mod3 <- run_control(set.vax.intro.date= vax.intro.date, set.form_cont1=form_control)

summary(mod3$mod1)

mod3$mod1$aic #AIC score

```
format the outputs, generate plots

```{r}
mod3.outputs <- control_outputs(fitted.mod=mod3,months.start=months_until_second_knot,
                                set.vax.intro.date=vax.intro.date,set.months_until_second_knot=months_until_second_knot)
```

Rate ratio for eval period

```{r}
mod3.outputs$rr.q.post

```

Rate ratio at each time points

```{r}
mod3.outputs$p.rr.trend
```

Observed vs expected by month
```{r}
mod3.outputs$p.preds
```

Observed vs expected by year
```{r}
mod3.outputs$p.preds.agg
```

```{r}
ggplotly(mod3.outputs$p.cum_prevented)
```







